### 2020-05-08 inst/examples/benchmarking-backends.Rmd
replacing readr with base

@@

```{r read}
# ref <- contentid::resolve("hash://sha256/86df0d24994a34dfc5e638f8b378c1b6d52ff1a051c12d93aa04984c15bf9624")
ref <- contentid::resolve("hash://sha256/598032f108d602a8ad9d1031a2bdc4bca1d5dca468981fa29592e1660c8f4883")
df <- read.delim(ref, stringsAsFactors = FALSE)

# In-memory queries

Focus on a key-value pairing here

```{r}
df <- dplyr::select(df, url = contentURL, id = checksum)
ex <- sample(df$url, 1e3)
```

@@

bench_time({ # 173ms
  id0 <- df[df$url %in% ex,]$id
})

@@

```{r dplyr}
library(dplyr)
bench_time({ # 
  id1 <- df %>% filter(url %in% ex) %>% pull(id)
})
identical(id0, id1)

@@

@@

```{r duckdb}
# install.packages("duckdb", repos=c("http://download.duckdb.org/alias/master/rstats/", "http://cran.rstudio.com"))
library(duckdb)
ddir <- tempfile()
con <- DBI::dbConnect( duckdb::duckdb() , dbdir = ddir)
DBI::dbWriteTable(con, "df", df)

bench_time({
  id6 <- tbl(con, "df") %>% inner_join(tibble(url = ex), by="url", copy = TRUE) %>% pull(id)
})
bench_time({
  id6b <- tbl(con, "df") %>%  filter(url %in% ex) %>% pull(id)
})

dbDisconnect(con, shutdown=TRUE)
```

```{r}
identical(id0, id6)
identical(id0, id6b)
#fs::dir_info(ddir) %>% pull(size) %>% sum()

@@

@@

```{r monet}
# install.packages("MonetDBLite", repo = "https://cboettig.github.io/drat")
library(MonetDBLite)
mdir <- tempfile()
con <- DBI::dbConnect( MonetDBLite() , dbname = mdir)
DBI::dbWriteTable(con, "df", df)

bench_time({
  id7 <- tbl(con, "df") %>% inner_join(tibble(url = ex), copy = TRUE) %>% pull(id)
})
bench_time({
  id7b <- tbl(con, "df") %>%  filter(url %in% ex) %>% pull(id)
})

dbDisconnect(con, shutdown=TRUE)
rm(con)
```

```{r}
identical(id0, id7)
identical(id0, id7b)
#fs::dir_info(mdir) %>% pull(size) %>% sum()
```

>>>>

knitr::opts_chunk$set(error=TRUE)
```

@@

```{r read}
ref <- contentid::resolve("hash://sha256/598032f108d602a8ad9d1031a2bdc4bca1d5dca468981fa29592e1660c8f4883")
df <- read.delim(ref, stringsAsFactors = FALSE)

df <- dplyr::select(df, url = contentURL, id = checksum)
ex <- sample(df$url, 1e6)
```

@@

bench_time({
  id0 <- df[df$url %in% ex,]$id
})

@@

```{r dplyr}
library(dplyr)
bench_time({
  id1 <- df %>% filter(url %in% ex) %>% pull(id)
})
identical(id0, id1)

@@

## Thor

@@

```{r duckdb}
# install.packages("duckdb", repos=c("http://download.duckdb.org/alias/master/rstats/", "http://cran.rstudio.com"))
library(duckdb)

ddir <- fs::path(fs::path_temp(), "duckdb", "duckdb1")
fs::dir_create(fs::path_dir(ddir))
con <- DBI::dbConnect( duckdb::duckdb(), dbdir = ddir)
DBI::dbWriteTable(con, "df", df)

bench_time({
  id6 <- tbl(con, "df") %>% inner_join(tibble(url = ex), by="url", copy = TRUE) %>% pull(id)
})
identical(id0, id6)

@@

```{r duckdb-filter}
bench_time({
  id6b <- tbl(con, "df") %>%  filter(url %in% ex) %>% pull(id)
})
identical(id0, id6b)
```

```{r}
dbDisconnect(con, shutdown=TRUE)
fs::dir_info(fs::path_dir(ddir)) %>% pull(size) %>% sum()
```

@@

```{r monet}
# install.packages("MonetDBLite", repo = "https://cboettig.github.io/drat")
library(MonetDBLite)
library(DBI)
library(dplyr)

mdir <- tempfile()
con2 <- DBI::dbConnect( MonetDBLite() , dbname = mdir)
DBI::dbWriteTable(con2, "df", df)

bench_time({
  id7 <- tbl(con2, "df") %>% inner_join(tibble(url = ex), copy = TRUE) %>% pull(id)
})
identical(id0, id7)

```{r monetdb-filter}
### fails if ex is a big vector

# bench_time({
#  id7b <- tbl(con2, "df") %>%  filter(url %in% ex) %>% pull(id)
#  })
# identical(id0, id7b)

```{r}
DBI::dbDisconnect(con2, shutdown=TRUE)
rm(con2)
```

```{r}
fs::dir_info(mdir, recurse=TRUE) %>% pull(size) %>% sum()
```
